---
title: "Features and Elements of Multiple Regression"
author: "Stuart McColl"
date: "06/01/2021"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 1

### Load the diamonds.csv data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant Kaggle page

```{r, warning=FALSE, message=FALSE}

library(tidyverse)
library(mosaicData)
library(GGally)
library(ggfortify)
library(mosaic)
library(fastDummies)

diamonds <- read_csv("/Users/Natifu/codeclan_homework_StuartM/week_10/day_2/4_diamonds_hw/data/diamonds.csv")

```

```{r}

glimpse(diamonds)

```

<br>

# Part 2

### We expect the carat of the diamonds to be strong correlated with the physical dimensions x, y and z. Use ggpairs() to investigate correlations between these four variables.

```{r, warning=FALSE, message=FALSE}

diamonds %>% 
  select(carat, x, y, z) %>% 
  ggpairs(diamonds)

```

<br>

# Part 3

### So, we do find significant correlations. Let’s drop columns x, y and z from the dataset, in preparation to use only carat going forward.

```{r}

diamonds <- diamonds %>% 
  select(-x, -y, -z)

glimpse(diamonds)

```

<br>>

# Part 4.1

### We are interested in developing a regression model for the price of a diamond in terms of the possible predictor variables in the dataset.

### Use ggpairs() to investigate correlations between price and the predictors (this may take a while to run, don’t worry, make coffee or something).

```{r}

ggpairs(diamonds)

```

# Part 4.2

### Perform further ggplot visualisations of any significant correlations you find.

```{r}

diamonds %>% 
  ggplot(aes(x = price, y = carat)) +
  geom_point(colour = "#484848") +
  geom_smooth(method = "lm", se = FALSE, colour = "#b38600") +
  theme_light()

```

# Part 5








