---
title: "Features and Elements of Multiple Regression"
author: "Stuart McColl"
date: "06/01/2021"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 1

### Load the diamonds.csv data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant Kaggle page

```{r, warning=FALSE, message=FALSE}

library(tidyverse)
library(mosaicData)
library(GGally)
library(ggfortify)
library(mosaic)
library(fastDummies)

diamonds <- read_csv("data/diamonds.csv")

```

```{r}

glimpse(diamonds)

```

<br>

# Part 2

### We expect the carat of the diamonds to be strong correlated with the physical dimensions x, y and z. Use ggpairs() to investigate correlations between these four variables.

```{r, warning=FALSE, message=FALSE}

diamonds %>% 
  select(carat, x, y, z) %>% 
  ggpairs(diamonds)

```

<br>

# Part 3

### So, we do find significant correlations. Let’s drop columns x, y and z from the dataset, in preparation to use only carat going forward.

```{r}

diamonds <- diamonds %>% 
  select(-x, -y, -z)

glimpse(diamonds)

```

<br>

# Part 4.1

### We are interested in developing a regression model for the price of a diamond in terms of the possible predictor variables in the dataset.

### Use ggpairs() to investigate correlations between price and the predictors (this may take a while to run, don’t worry, make coffee or something).

```{r}

ggpairs(diamonds)

```

<br>

# Part 4.2

### Perform further ggplot visualisations of any significant correlations you find.

```{r}

diamonds %>% 
  ggplot(aes(x = carat, y = price)) +
  geom_point(colour = "#484848") +
  geom_smooth(method = "lm", se = FALSE, colour = "#b38600") +
  theme_light()

```

<br>

# Part 5.1

### Shortly, we may try a regression fit using one or more of the categorical predictors; cut, clarity and color, so let’s investigate these predictors:

### Investigate the factor levels of these predictors. How many dummy variables do you expect for each of them?

```{r}

diamonds %>% 
  distinct(cut) 

diamonds %>% 
  distinct(color)

diamonds %>% 
  distinct(clarity)


```

<br>

# Part 5.2

### Use the dummy_cols() function in the fastDummies package to generate dummies for these predictors and check the number of dummies in each case.

```{r}

diamonds_dummy <- diamonds %>% 
  dummy_cols(select_columns = c("cut", "color", "clarity"), remove_first_dummy = TRUE,
             remove_selected_columns = TRUE)

diamonds_dummy

```

<br>

# Part 6.1

### Going forward we’ll let R handle dummy variable creation for categorical predictors in regression fitting (remember lm() will generate the correct numbers of dummy levels automatically, absorbing one of the levels into the intercept as a reference level)

### First, we’ll start with simple linear regression. Regress price on carat and check the regression diagnostics.

```{r}

diamonds_model1 <- lm(price ~ carat, data = diamonds)

summary(diamonds_model1)

```

### Therefore, if carat goes up by a factor of 1, then price goes up by 7,756

<br>







