---
title: "Logistic Regression Homework"
author: "Stuart McColl"
date: "16/01/2021"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load in libraries and data

```{r, message=FALSE, warning=FALSE}

library(car)
library(tidyverse)
library(modelr)
library(GGally)
library(relaimpo)
library(lm.beta)
library(leaps)
library(glmulti)
library(caret)
library(janitor)
library(lubridate)


orange_juice_raw <- read_csv("data/orange_juice.csv") %>% 
  clean_names()

```

# Check out the data

```{r}

summary(orange_juice_raw)
glimpse(orange_juice_raw)

```

purchase column - change to logical
weekof_purchase - change to factor
store_id - change to factor
special_ch - change to logical
special_mm - change to logical
loyal_ch - remove
price_diff - remove, can be worked out with the other two variables
store7 - remove as store id includes store 7 
pct_disc_mm - remove
pct_disc_ch - remove
list_price_diff - remove
store - remove as store id is better, also includes store 7

```{r}

unique(orange_juice_raw$store_id)
unique(orange_juice_raw$store)


```


# Change column class for modelling

```{r}

orange_juice_clean <- orange_juice_raw %>% 
  mutate(purchase_mm = as.logical(if_else(purchase == "MM", T, F))) %>% 
  mutate(weekof_purchase = as_date(weekof_purchase)) %>% 
  mutate(store_id = as.factor(store_id)) %>% 
  mutate(special_ch = as.logical((ifelse(special_ch == 1, T, F)))) %>% 
  mutate(special_mm = as.logical(ifelse(special_mm == 1, T, F)))

glimpse(orange_juice_clean)


```

# Remove unhelpful columnns

```{r}

orange_juice_clean <- orange_juice_clean %>% 
  dplyr::select(-c(purchase, loyal_ch, price_diff, store7, pct_disc_mm, pct_disc_ch, 
            list_price_diff, store))

glimpse(orange_juice_clean)

```


# Change weekof_purchase into quarters

```{r}

orange_juice_clean <- orange_juice_clean %>% 
  mutate(
    quarter = as.factor(quarter(weekof_purchase))
  ) %>% 
  dplyr::select(-weekof_purchase)

glimpse(orange_juice_clean)


```


# Check for aliased columns

```{r}

alias(purchase_mm ~ ., data = orange_juice_clean)

```

# Remove aliased columns

```{r}

orange_juice_clean <- orange_juice_clean %>% 
  dplyr::select(-c(sale_price_mm, sale_price_ch))

alias(purchase_mm ~ ., data = orange_juice_clean)

```

# Check cleaned data

```{r}

glimpse(orange_juice_clean)

```















