---
title: "R Notebook"
output: html_notebook
---

# Homework - ggplot2 advanced

# Load Libraries

```{r}

library(tidyverse)
library(CodeClanData)

```


# Load Data

```{r}

qb_revenue_breakdown <- qb_revenue_breakdown
qb_monthly_sales <- qb_monthly_sales 
qb_competitors <- qb_competitors
qb_device_data <- qb_device_data

```


# View Data 

```{r}

head(qb_revenue_breakdown)
head(qb_monthly_sales)
head(qb_competitors)
head(qb_device_data)


```

# Load Colour Scheme

```{r}

col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

```


# Questions 

# Question 1

Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.


```{r}

qb_revenue_breakdown

ggplot(qb_revenue_breakdown) +
  aes(x = Year, y = Revenue, fill = "#50434F") +
  scale_fill_manual(values = "#50434F", guide = "none") +
  geom_col() +
  theme_light() +
  labs(title = "QikBit Revenue") 

?geom_bar

```

# Question 2 

Make a line chart showing monthly sales of the “flagship product” - the KwikBit Unit1 - over the last year. This data is inside qb_monthly_sales, but you will need to use subset.


```{r}

qb_monthly_sales

ggplot(qb_monthly_sales) +
  aes(x = Date, y = Amount, filter = Cashflow == "Kwikbit Unit 1 Sales", colour = Cashflow) +
  geom_line() +
  scale_colour_manual(
    values = c(
      "Cost" = "#E89FE9",
      "Kwikbit Unit 1 Sales" = "#50434F",
      "Total Revenue" = "#B6A7B5")) +
  theme_light()

?geom_line

```

# Question 3

Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}

ggplot(qb_monthly_sales) +
  aes(x = Date, y = Amount, filter = Cashflow == "Kwikbit Unit 1 Sales", colour = Cashflow) +
  geom_line() +
  scale_colour_manual(
    values = c(
      "Cost" = "#E89FE9",
      "Kwikbit Unit 1 Sales" = "#50434F",
      "Total Revenue" = "#B6A7B5")) +
  theme_light()

```

# Question 4

Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.


```{r}

qb_competitors

ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, fill = Company) +
  geom_area() +
  theme_light() +
  scale_fill_manual(
    values = c(
      "Competitor 1" = "#E89FE9",
      "Competitor 2" = "#50434F",
      "Competitor 3" = "#F9A472",
      "Competitor 4" = "#BD7040")) +
  labs(title = "Personal Fitness Tracker Sales")
  

?geom_area


```

# Question 5 

Now show the sales from the 5 competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}

qb_competitors

ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, colour = Company) +
  geom_line() +
  scale_colour_manual(
    values = c(
      "Competitor 1" = "#E89FE9",
      "Competitor 2" = "#50434F",
      "Competitor 3" = "#F9A472",
      "Competitor 4" = "#BD7040")) +
  geom_point() +
  theme_light() +
  labs(title = "Personal Fitness Tracker Sales")
  

```

# Question 6 

Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between individuals and people. Data is in qb_device_data.

```{r}

head(qb_device_data)

ggplot(qb_device_data) +
  aes(x = device, y = counts) +
  geom_line()

```




















