---
title: "R Notebook"
output: html_notebook
---

# Introduction to ggplot2 homework

# Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}

library(tidyverse)
library(CodeClanData)

```

```{r}

backpack <- backpack

```

```{r}

names(backpack)

```


```{r}

glimpse(backpack)

```

# Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.


```{r}

ggplot(backpack) +
  geom_bar(aes(x = backpack_weight), fill = "light blue")

```

From the graph above, you will see that there is a higher count of backpacks that are 10 and below. As the bag gets heavier, there is a smaller count.

# Question 3.

Are there differences in backpack weight between sex?

ggplot(students) +
  geom_bar(aes(x = superpower, fill = school_year), position = "dodge")

```{r}

ggplot(backpack) +
  geom_bar(aes(x = backpack_weight, fill = sex), position = "dodge")

```

From the results above, you will see that there is a higher count of backpacks for females. You can also see that there are specific weights that only the males are carrying - just over 10 is most popular and they do carry heavier bags compared to females.

# Question 4.

What is the relationship between body weight and backpack weight?

```{r}

ggplot(backpack) +
  geom_bar(aes(x = body_weight, y = backpack_weight), fill = "light blue", stat = "identity")
  

```

As you can see from the results above, there is a trend that as the body weight goes up to around 160, the weight of the backpack increases and then drops off.












