---
title: "R Notebook"
output: html_notebook
---

# step 1 - load libraries

```{r}

library(tidyverse)


```


# 1

Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}

codeclan_tweets <- read_csv("data/code_clan_tweets.csv")

names(codeclan_tweets) # see below

ncol(codeclan_tweets) # 27

nrow(codeclan_tweets) # 234

```

# 2

Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}

codeclan_favourite <- codeclan_tweets %>%
  filter(is_quote == FALSE) %>%
  summarise(sum_of_fave_tweets = sum(favorite_count))
  

```

# 3

Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.


```{r}

codeclan_retweet <- codeclan_tweets %>%
  filter(is_quote == FALSE) %>%
  group_by(source) %>%
  summarise(mean_of_retweets = mean(retweet_count))

```


# 4

Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.


```{r}

codeclan_likes <- codeclan_tweets %>%
  mutate(media_type = coalesce(media_type, na.rm = "text")) %>% 
  group_by(media_type) %>%
  summarise(sum_of_likes = sum(favorite_count)) %>%
  arrange(desc(sum_of_likes))
  

```


# 5

Find the mean number of characters that a CodeClan tweet contains.

```{r}

codeclan_mean <- codeclan_tweets %>%
  summarise(mean_of_tweets = mean(display_text_width))
  
```


# 6

The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}

codeclan_info <- read_csv("data/code_clan_info.csv")

  joined_table <- left_join(codeclan_info, codeclan_tweets, by = "tweet_id")

```

# 7

From your new joined data, create a new tibble codeclan_hashtags containing only 
the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.


```{r}

codeclan_hashtags <- joined_table %>%
  select(tweet_id, hashtags) %>%
  mutate(hashtags = str_to_lower(hashtags)) %>%
  mutate(tweet_id = str_to_lower(tweet_id)) %>% 
  drop_na(hashtags)
  

```

















































