---
title: "R Notebook"
output: html_notebook
---

# Weekend Homework: dplyr

Data File | Goodreads-books
Brief Description | comprehensive list of all books listed in goodreads

# Stage One - Load Libraries

```{r}

library(tidyverse)
library(lubridate)

```

# Stage Two - Read in the 'books.csv' File and Assign to the Environment

```{r}

goodreads_books <- read_csv("data/books.csv")

```

# Stage Three - Basic Observations

```{r}

view(goodreads_books) 

# this allows you to view the entire data set

dim(goodreads_books) 

# this checks how many rows and columns in the data set

names(goodreads_books) 

# this tells you what the column titles are

head(goodreads_books, 10) 

# this gives you the first 10 rows by default

tail(goodreads_books, 10) 

# this gives you the last 10 rows by default

```

# Stage Four - Missing Data - General

```{r}

goodreads_books %>% 
  filter(is.na(goodreads_books)) 

# this function filters the data to check for any 'NAs'

```

# Stage Five - Select Function - General

```{r}

select(goodreads_books, title, average_rating)

# this function selects specific columns to view

```

# Stage Six - Filter Function - Stephen King

```{r}

  filter(goodreads_books, authors == "Stephen King",
       ratings_count > 100000
       & average_rating >= 4)
  

# this function allows you to filter and view all Stephen King books that
# have a ratings count of over 100,000
# AND have an average rating that equal to 4 and above

```

# Stage Seven - Arrange Function - Stephen King

```{r}

top_five_stephen_king <- goodreads_books %>%
  filter(authors == "Stephen King",
       ratings_count > 100000
       & average_rating >= 4) %>% 
  arrange(desc(average_rating)) %>% 
  select(title, authors, average_rating, ratings_count)

# this function allows you to arrange the average rating by 
# descending order AND select four specific columns

```

# Stage Eight - Mutate Function Stephen King

```{r}

top_five_stephen_king <- top_five_stephen_king %>%
  filter(authors == "Stephen King",
       ratings_count > 100000
       & average_rating >= 4) %>% 
  arrange(desc(average_rating)) %>% 
  select(title, authors, average_rating, ratings_count) %>% 
  mutate(
    high_or_low_rating_count = case_when(
      ratings_count < 250000 ~ "Low",
      ratings_count >= 250000 ~ "High"))

# this function adds a new column that tells you what book 
# has had a 'high' number of ratings or a 'low' number of ratings

```

# Stage Nine - Mutate Function - General

```{r}

goodreads_books_rating_count <- goodreads_books %>% 
mutate(
  high_or_low_rating_count = case_when(
  ratings_count < 500000 ~ "Very Low Count",
  ratings_count < 1000000 ~ "Low Count",
  ratings_count < 1500000 ~ "Medium Count",
  ratings_count < 2000000 ~ "High Count",
  ratings_count >= 2000000 ~ "Very High Count"
  )
)
         
# this function groups the ratings count in increments of 500,000
# a ratings count up to 500,000 is very low
# a ratings count from 500,000 to 1 million is low
# a ratings count from 1 million to 1.5 million is medium
# a ratings count from 1.5 million to 2 million is high AND
# a ratings count over 2 million is very high

```
# Stage Ten - Top Five ALL Books

```{r}
top_five_books <- goodreads_books_rating_count %>% 
  filter(high_or_low_rating_count == "Very High Count",
       average_rating >= 4) %>% 
  arrange(desc(average_rating)) %>% 
  head(5) %>% 
  select(title, authors, average_rating, ratings_count, high_or_low_rating_count)

```

# Stage Eleven - Top Five 90's Books

```{r}

goodreads_books_dates <- goodreads_books_rating_count %>% 
mutate(publication_date = (mdy(publication_date)))

top_five_90s <- goodreads_books_dates %>%
  filter(publication_date >= "1990-01-01" &
           publication_date <= "1999-12-29",
         ratings_count > 850000) %>% 
  arrange(desc(average_rating)) %>% 
  select(title, authors, average_rating, ratings_count, high_or_low_rating_count)

```

# Stage Twelve - Top Five Penguin Books

```{r}

top_five_penguin_books <- goodreads_books_dates %>%
    filter(publisher %in% c("Penguin", "Penguin Classics", "Penguin Books",
                            "Penguin Books Ltd", "Penguin Press"), 
           ratings_count > 800000) %>%
  arrange(desc(average_rating)) %>% 
  select(publisher, title, authors, average_rating, ratings_count, 
         high_or_low_rating_count)
  
```

# Stage Thirteen - Top Five Reviewed

```{r}

top_five_reviewed <- goodreads_books_rating_count %>%
  filter(text_reviews_count >= 30000, 
         ratings_count >= 1700000) %>%
  arrange(desc(average_rating)) %>%
  select(title, authors, publisher, text_reviews_count, average_rating, 
         ratings_count, high_or_low_rating_count)
  

```
















