---
title: "SQL Day 2 Lab and Homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r, eval=TRUE, include=FALSE, message=FALSE, warning=FALSE}
library(RPostgres)

db = dbConnect(
  Postgres(), 
  user = 'omni_user',
  password = 'in2z00yfv3as3hgo',
  dbname = 'omni_pool',
  host = 'db-postgresql-lon1-94437-do-user-4831272-0.a.db.ondigitalocean.com',
  port = 25061,
  sslmode = 'allow',
  bigint = "numeric"
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

**Duration - 120 minutes**  

In these practice questions you'll return again to the `omni_pool` database, so re-establish your connection in `DBeaver` if it has lapsed. 

<br>
<div class='emphasis'>
**Submission**

When answering these questions, please save your `SQL` script in `DBeaver`, copy it over to your homework repo and then add, commit and push that for submission tonight. Please add section and question numbers as `SQL` comments, like so:

```{sql, eval=FALSE}
--MVP
--Q1
```
</div>
<br>

# MVP Questions

1. Get a table of all `employees` details, together with their `local_account_no` and `local_sort_code`, if they have them.

<details>
<summary>**Hints**</summary>  

* `local_account_no` and `local_sort_code` are fields in `pay_details`, and employee details are held in `employees`, so this query requires a `JOIN`.
* What sort of `JOIN` is needed if we want details of **all** employees, even if they don't have stored `local_account_no` and `local_sort_code`?

</details>
<br>

2. Amend your query from question 1 above to also return the `name` of the team that each employee belongs to.

3. Find the first name, last name and team name of employees who are members of `teams` for which the charge cost is greater than 80. Order the employees alphabetically by last name.  

<details>
<summary>**Hints**</summary>  

* `charge_cost` may be the wrong type to compare with value `80`. Can you find a way to convert it **without changing** the database? 
* This query will require a `JOIN`, with a `WHERE` clause on a field in `teams`.

</details>
<br>

4. Breakdown the number of employees in each of the `teams`, including any `teams` without members. Order the table by increasing size of team.  

<details>
<summary>**Hints**</summary>   

* Two tables involved here, so a `JOIN` is necessary.
* We want to include **all teams** (not just those with member employees), so an `INNER JOIN` won't work...
* We need to `GROUP BY` team name and count the number of employees in each team.

</details>
<br>

5. The `effective_salary` of an employee is defined as their `fte_hours` multiplied by their `salary`. Get a table for each employee showing their `id`, `first_name`, `last_name`, `fte_hours`, `salary` and `effective_salary`, along with a running total of `effective_salary` with employees placed in ascending order of `effective_salary`.  

<details>
<summary>**Hint**</summary> 
A window function is probably the easiest way to do this.
</details>
<br>

6. The `total_day_charge` of a team is defined as the `charge_cost` of the team multiplied by the number of `employees` in the team. Calculate the `total_day_charge` for each team.

<details>
<summary>**Hints**</summary> 

* If you `GROUP BY teams.id`, because it's the primary key, you can `SELECT` any other column of `teams` that you want (this is an exception to the rule that normally you can only `SELECT` a column that you `GROUP BY`).
* You can also tackle this efficiently using a CTE.

</details>
<br>

7. How would you amend your query from question 6 above to show only those `teams` with a `total_day_charge` greater than 5000?

# Extension Questions

1. How many of the employees serve on one or more committees?  

<details>
<summary>**Hints**</summary> 

* All of the details of membership of committees is held in a single table: `employees_committees`, so this doesn't require a join.
* Some employees may serve in multiple committees. Can you find the number of distinct employees who serve? [**Extra hint** - do some research on the `DISTINCT()` function].

</details>
<br>

2. How many of the employees do not serve on a committee?  

<details>
<summary>**Hints**</summary>   

* This requires joining over only two tables
* Could you use a join and find rows without a match in the join?
* [**Tough!**] Can you modify your query from the previous question to do this? [**Extra hint** - perhaps try two subqueries, or perhaps two CTEs with a `CROSS JOIN` to combine them]

</details>
<br>

<br>
<p style="margin-left: 60px; margin-right: 60px">
**The following problems require joining over three tables: `employees`, `committees` and the join table `employees_committees`. Again, don't worry, take it slow and think of the join of the first two tables producing a table that we *then* join to the third table.**
</p>
<br>

3. Get the full employee details (including committee name) of any committee members based in China.  

<details>
<summary>**Hints**</summary>

* We need both joins for the many-to-many relationship with a join table.
* We need to filter based upon the country of employees 

</details>
<br>

4. **[Tough!]** Group committee members into the `teams` in which they work, counting the number of committee members in each team (including teams with no committee members). Order the list by the number of committee members, highest first.  

<details>
<summary>**Hints**</summary>

* Again, you probably want to count `DISTINCT()` employees.
* This requires **three** joins: two joins for the many-to-many relationship as usual, followed by a third join to `teams`!
* 'including teams with no committee members' - what type of join should we create to `teams`?

</details>
<br>

